On existence of integral point sets and their diameter bounds \footnote{ This work was carried out at Voronezh State University and supported by the Russian Science Foundation grant 19-11-00197. }

### 2020-01-02 pps-linear-bound/pps-linear-lower-bound.tex
[J220] Improving the section structure

@@

@@

@@

In this section,
we improve the lower bound for minimum diameter of planar integral point sets
employing Point Packing in a Square problem.
Below we introduce the problem, basic notions and results.

@@

To prove the bound on $d(2,n)$, we also need the following results and notions from~\cite{our-vmmsh-2018}.

@@

@@

Now we need to estimate the cardinality of an intersection of an integral point set with a line segment.

>>>>

TODO: note about Section structure.

@@

\subsection{General results}

@@

\subsection{Special results}

@@

\section{Planar integral point set in a square}

In this section, we develop some methods that employ the fact that every planar integral point set is situated in a square.
Then we establish a connection between distances in integral point sets and the Point Packing in the Square problem.

\subsection{General results}

Let us introduce the Problem, basic notions and results.

@@

Now we will estimate the side length of a square which contains a given planar integral points set.

@@

\subsection{Special results}

In this section,
we improve the lower bound for minimum diameter of planar integral point sets
employing the results of two previous sections.

\subsection{General results}

@@

\subsection{Special results}
